Towards Compiler-Agnostic Performance in Finite-Difference Codes

### 2015-09-15 docs/papers/shallow_performance/shallow_perf.tex
parco paper: more work on explicitly using numbering of transformations

Beginning with the vanilla \psykal\ version, we then manually apply a
series of (cumulative) code transformations while obeying the \psykal
separation of concerns, {\it i.e.} optimisation is restricted to the
middle, {PS}y layer and leaves the kernel and algorithm layers
unchanged. The aim of these optimisations is to recover, as much as is
possible, the structure and thus performance of the original version
of the code. We began with two transformations that affect all of the
kernels. After this, we determined the transformations to perform by
comparing the timing profiles of the \psykal\ and original versions of
the code. We then tackled the sections resposible for the largest
slowdowns and iterated this process. While doing this we also made
heavy use of the optimisation reports produced by the compilers and
how these changed when moving from the original to the \psykal\ version
of the code.

@@

@@

As indicated above, the last two of these transformations were
suggested by the IBM compiler team. The second of these effectively
undoes our 3rd transformation by fissioning the first loop nest back
into three separate loop nests.

>>>>

Beginning with the vanilla \psykal\ version, we then manually apply a
series of (cumulative) code transformations while obeying the \psykal\ 
separation of concerns, {\it i.e.} optimisation is restricted to the
middle, {PS}y layer and leaves the kernel and algorithm layers
unchanged. The aim of these optimisations is to recover, as much as is
possible, the structure and thus performance of the original version
of the code. We began with two transformations that affect all of the
kernels. After this, we determined the transformations to perform by
comparing the timing profiles of the \psykal\ and original versions of
the code. We then tackled the sections resposible for the largest
slowdowns and iterated this process. While doing this we also made
heavy use of the optimisation reports produced by the compilers and
how these changed when moving from the original to the \psykal\ version
of the code.

@@

\item No optimisation: the vanilla \psykal\ version of the code;

@@

As indicated above, transformations 10 and 11 were
suggested by the IBM compiler team. The second of these effectively
undoes transformation four by fissioning the first loop nest back
into three separate loop nests.
